Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-08 Ben_Manuscripts/structure_paper/Draft.tex
Updates

  Evidence strongly suggests that the R-spots signal is not a result of alkane chain tilt. 
  Previous literature has attributed the spots in this particular WAXS pattern as the product 
  of tilted alkane chains~\cite{feng_scalable_2014}. We measured the tilt angle of the
  alkane chains of the 280K system and showed that it equilibrates to an average tilt angle of
  -2\degree (Fig.~\ref{fig:tilt}), far from the 37\degree tilt angle previously used to 
  explain R-spots. 
  %MRS8: did you do a few different things here as sensitivity analysis to show that the finding was robust?  If so, putting some of that in would be useful.
  %BJC7: make it clear that it is the 280K. Reference all configurations where tilt angles were calculated.

  To understand the most likely origin of R-spots, we determined which atoms
  gave rise to the feature. 
  %MRS8: next two sentences repetitive; could you revise? 
%  Since R-spots is present as higher intensity spots within R-alkanes, it is
%  likely that the spots arise as a consequence of the tails. 
  By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the cause
  of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the tails stay
  nearly flat, we plotted their centroids (Figure \ref{fig:centroids}) and
  measured the angle between each centroid and its nearest neighbors with respect
  to the plane of the membrane. We see distinct peaks in the distribution of
  these angles (Figure~\ref{fig:tail_packing}).

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.32\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.png}
  	\caption{}\label{fig:sandwiched280K}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \includegraphics[width=\textwidth]{tilt_dist.png}
    \caption{}\label{fig:tilt}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
	\centering
	\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
	\caption{}\label{fig:tails_rzplot}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
    \centering
	\includegraphics[width=\textwidth]{centroids_box.png}
  \caption{}\label{fig:centroids}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
        \centering
	        \includegraphics[width=\linewidth]{angles_traj_layered.png}
	        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
        	\centering
	        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
	        \caption{}~\label{fig:layered_integration}
  \end{subfigure}
  \caption{(a) R-spots increases in intensity when the temperature of the system is 
      lowered to 280K. (b) We measured the average angle made between each monomer 
      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
      near -2\degree~which is far from the 37\degree~tilt angle previously used to
      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
      from the trajectory except for carbon atoms that constitute the tails. The
      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
      Since the tails stay relatively flat, we plotted the centroid of each tail 
      and observed that they pack hexagonally (for example, green colored centroids
      in the plot surround the red centroid in hexagonal fashion). (e) We hypothesize
      that R-spots is the result of ordered tail packing. Defining
      the membrane plane to be 0\degree, we measured the angles between each alkane 
      chain tail centroid and its nearest neighbor centroids for the equilibrated 
      sandwiched configuration simulated at 280K. Peaks that appear in each distribution
      are centered near $\pm~33\degree$. (f) We radially integrated the simulated XRD
      patterns of the parallel displaced and sandwiched configuration within the region
      bounding R-alkanes. Peaks appear in the same location as the angle distributions
      which corroborates our hypothesis.}~\label{fig:tail_packing}
  \end{figure}

@@

  The intensity of R-$\pi$ can be calculated from a single trajectory of uncorrelated
  configurations rather than as the average of multiple correlated trajectories. Theoretically,
  in order to mimic the simulated system, we should build an initial configuration which 
  has the same amount of quenched disorder as our simulations and then create a trajectory
  to which we add thermal disorder to the initial configuration in order to create each frame.
  %BJC9 : The following numbers need to be updated: I want to do 40 trajectories with 1000 frames each for both types of trajectories and compare their mean and uncertainty
  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this way was 
  16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000 initial configurations,
  the intensity of R-$\pi$ is 16.42, in close agreement with the mean of 40 simulations. 
  We use the latter method for the remainder of this work since we can extract the trends
  we need using a single trajectory at a fraction of the computational cost.

  When we simulated the diffraction pattern of a simple system trajectory of 1000 independent
  configurations, each created using the parameters for thermal and quenched disorder in order to place 
  points, the $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
  this simple system, and all to follow, 4 times taller in the $z$-direction in order to access
  higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation} and~\ref{fig:sf_qz_correlation}
  shows the $q_y$ and $q_z$ cross-sections of R-$\pi$ generated by simulating the structure 
  factor of the trajectory. The distance between peaks in the $q_y$ cross-section is equal
  to the distance between pores in real space.

@@

  %BJC8: Create parallel displaced configuration: create sandwiched system. Apply uniform rotation to every other layer
  %BJC8: I'd like to make the point somewhere that the real configuration is somewhere between sandwiched and the
  % parallel displaced configuration shown here.
  %MRS9: better to say ``data is most consistent with the idea that the real configuration is somewhere between''

%MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
%BJC9: haha^
%BJC9: I could probably get rid of qy cross-sections and inset in (c)
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
  \caption{}\label{fig:sf_qy_nocorrelation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
  \caption{}\label{fig:sf_qy_correlation}
  \end{subfigure} 
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
  \caption{}\label{fig:sf_qz_correlation}
  \end{subfigure}   
  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
  points meant to represent monomer head groups. We added a similar amount of noise to 
  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
  peaks. (b) When we correlate the distance between points within each column, the 
  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
  intensity between the center and outer peaks. (c) Correlation of the distance between
  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
  \end{figure}

  The distances between scatterers within each column are correlated with each other.
  In the simplified system described above, we added Gaussian noise to the 
  mean positions of an equally spaced column of points. This ignores any interaction
  head groups might have with each other. To remedy this, we drew random samples from 
  a multivariate normal distribution defined by the mean positions of an equally spaced
  column of points. We gave the distribution at each point along the column the same
  standard deviation, $\sigma_z$, shown  in by Table~\ref{table:quenched_disorder}. We 
  defined a covariance matrix such that the covariance, v, in the distance, z, between
  scatterers decays exponentially from v according to the equation $ve^{-z/L}$, where L
  is the correlation length. Experimentally, the correlation length can be estimated as
  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$.  %BJC8: needs references 
  Accordingly, the correlation length of the experimental system is $\geq$ 9 
  $\AA$. The value may be larger since the peak is likely broadened for a variety
  of other reasons. We simulated the structure factor of a simple system built as described
  above with a correlation length of 30 $\AA$. We chose 30 $\AA$ in order to exaggerate
  the effect of correlation length for visual purposes. Subsequent structure factor calculations
  are all done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section 
  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$ cross-section
  (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in experiment. Additionally, there
  is a near 20 \% increase in the maximum intensity of R-$\pi$ when the distances between
  scatterers are correlated.

@@

  %BJC8: The next couple paragraphs is all old stuff that can likely be cut down a bit. But I think 
  % this is where I'd put this discussion.
  Monomers in the ordered basin stack closer together than those in the disordered basin
  (Table~\ref{table:correlation_length}). We calculated the equilibrated vertical distance,
  $\mathit{d}_{equil}$, between monomers using Equation~\ref{eqn:decaying_sinusoid}. 
  Monomers in the ordered basin stack ca. 0.2 and 0.3 \AA~closer than those built in the 
  disordered basin in the sandwiched and parallel displaced configurations respectively. 
  The distance between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all 
  cases, with disordered basins at the high part of that range, 0.2 and 0.3 \AA~more distant.
  %MRS9: GAFF could OVER predict pi-pi stacking, best to include citations here that it does indeed overpredict.
  %BJC9: Turns out the Jankowski group was using oplsaa, not GAFF (they said GAFF to me). Will search for other
  % references.
  This behavior is not surprising since GAFF models atoms as point charges and does not 
  appropriately model the aromatic $\pi-\pi$ interactions which would make it more energetically
  favorable for the monomers to stack closer together. Additionally, it is possible that the 
  tails prevent close stacking of monomer head groups and we do not achieve the timescales 
  necessary for them to rearrange into a necessarily more tightly packed configuration. Since 
  ordered basin systems pack closest together, they are likely the best choice for transport 
  studies.

@@

  The correlation length of the parallel displaced, ordered basin system shows
  the closest agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
  correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
  not extract a reliable correlation length from the disordered parallel displaced configuration
  since the peaks do not show clear patterns that can easily be fit to an exponential decay. The 
  correlation length of both sandwiched systems is relatively low because the height of the first
  peak of $g(z)$ is so high. The peak height indicates the degree of local ordering and influences
  the intensity of R-$\pi$. If vertically adjacent sandwiched head groups were less ordered, which
  might be achieved with much longer simulations, then the leading peak intensity should decrease and
  the correlation length would increase. We expect that the leading peak would only get more intense 
  if monomers stacked 3.7 \AA~apart. Conversely, parallel displaced head groups are not as confined
  by their vertically adjacent neighbors. This z-direction translational freedom may still be 
  feasible if monomers stack 3.7 \AA~apart in a parallel displaced configuration, meaning the system
  would maintain a correlation length and R-$\pi$ intensity in relative agreement with experiment.

@@

  % BJC9: Might be worth acknowledging:
  % The peaks are spaced apart according to the pore spacing, and line up with R-alkanes.

%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.3\textwidth}
%  \includegraphics[width=\textwidth]{sf_qy_correlation_L10.png}  %BJC9: z_variance = 2.074 angstroms
%  \caption{}\label{fig:sf_znoise_control}
%  \end{subfigure}
%  \begin{subfigure}{0.3\textwidth}
%  \includegraphics[width=\textwidth]{sf_qy_3xdecrease.png}  %BJC9: z_variance = 2.65 angstroms
%  \caption{}\label{fig:3xdecrease}
%  \end{subfigure}
%  \begin{subfigure}{0.3\textwidth}
%  \includegraphics[width=\textwidth]{sf_qy_15xdecrease.png}  %BJC9: z_variance = 3.4 angstroms
%  \caption{}\label{fig:15xdecrease}
%  \end{subfigure}
%  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
%  however the $q_r$ cross-section profile does not change. (a) The maximum intensity of R-$\pi$ is ca. 20 
%  when we use the same level of noise present in the atomistic simulation. (b) The intensity of R-$\pi$ 
%  decreases by a factor of 3, relative to the background intensity, if we increase thermal noise by 11\% 
%  in the $z$-direction. (c) The intensity of R-$\pi$ decreases by a factor of 15, relative to the background
%  intensity, when we increase thermal noise by 28\% in the $z$-direction.}\label{fig:znoise}
%  \end{figure}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
  however the $q_r$ cross-section profile does not change. (a) The intensity of R-$\pi$ drops precipitously
  as we increase $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the background intensity
  as seen in our simulation (blue) by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase 
  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$ decreases with increasing $\sigma_z$,
  the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  When we allow monomer columns to move independently in the z-direction, the intensity
  of R-$\pi$ drops and the $q_r$ cross-section of the simulated diffraction patterns 
  smooths out. We created simple systems with varying amounts of association between columns. 
  In the low limit, the center of mass of columns are situated at the same $z$-coordinate. 
  This is how all simple systems have been created up to this point. We allow increasing 
  independence of columns by randomly shifting each column in the $z$-direction using a uniform
  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We
  limit this discussion to the sandwiched configuration since it is not
  feasible for columns in the parallel displaced configuration, as we have set them up, to move
  past each other. The trends seen above apply to both the sandwiched and parallel displaced systems.
  Allowing columns to move independently smooths out the $q_r$ cross-section
  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp peaks. The
  intensity of R-$\pi$ decreases with increasing column independence. We see an 8-fold decrease
  in the intensity of R-$\pi$ when $f=1$ versus when $f=0$.

  \begin{figure}
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr0.png}
  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr75.png}
  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr100.png}
  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
  \end{subfigure}
  \caption{As we increase column independence using the $f$ parameter, the intensity of R-$\pi$
  decreases and the $q_r$ cross-section of the simulated diffraction pattern becomes more smooth.
  (a) When we place all columns at the same z coordinate, $f$ = 0, the intensity of R-$\pi$ is
  18.3 and is characterized by sharp Bragg-like peaks. (b) When columns have a moderate amount of
  independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold to 3.7. The edges of the
  peak are beginning to smooth out, but sharp peaks still exist. (c) When columns are completely
  independent, $f$ = 1, the intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
  relatively smooth.}\label{fig:column_displacement}
  \end{figure}

  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$ cross-section of 
  R-$\pi$ to decrease. We modified the disorder in both the $r$ and $\theta$ directions by
  multiplying their values by a factor of 0.5 and 2 (Figure~\ref{fig:qy_fwhm}). When we cut
  the noise in half, the FWHM increases by 88 \%. When we double the noise, the FWHM 
  decreases by 51 \%.

@@

  We can use what we learned above in order to construct a better model, however there
  will still be shortcomings. We can decrease the intensity of R-$\pi$ if we incorporate
  more $z$-directional noise, which may come from increasing the system's temperature.
  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
  % temperature? Is decreasing the force constant between bonds viable? 
  We can adjust the parameters for aromatic carbons so that head groups stack more 
  closely together. Perhaps the simplest thing to do is to create initial configurations
  whose columns are displaced randomly in the $z$-direction in order to mimic independence.
  Ultimately, we will need extremely long simulation times so that monomers within 
  columns can rearrange and sample enough independent configurations to generate a robust
  simulated XRD pattern.

  The architecture of each column is likely somewhere between sandwiched and parallel 
  displaced. The parallel displaced configuration that we have simulated in this paper
  is an exaggerated manifestation of the parallel displaced $\pi-\pi$ stacking mode. 
  The simulated XRD pattern shows faint off-axis features at the same $q_r$ value as
  R-double which is only in patterns generated from parallel displaced configurations. 
  The monomers may prefer to be parallel displaced, but their displacement is likely 
  only slightly shifted, on the $xy$ plane, from the center of mass of their vertically
  adjacent neighbors. In this way, columns can more easily act independently while 
  maintaining a parallel displaced structure.

%  \item Stacked disks (layers)
%	  \item No influence on intensity
%	  \item Some influnce on FWHM (?)

%  There is not a single reason we can clearly identify for the high intensity of R-$\pi$ in our simulations.
%  We used one-dimensional pair distribution functions of the centers of masses of monomer
%  phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
%  columns and the degree to which they are correlated. These metrics helped us dissect the 
%  various contributions to R-$\pi$. Figure~\ref{fig:correlation} shows $g(z)$ for all 
%  systems tested.

>>>>

  Evidence strongly suggests that the R-spots signal is not a result of alkane
  chain tilt.  Previous literature has attributed the spots in this particular
  WAXS pattern as the product of tilted alkane chains~\cite{feng_scalable_2014}.
  We measured the tilt angle of the alkane chains of the 280K system and showed
  that it equilibrates to an average tilt angle of
  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. 
  %MRS8: did you do a few different things here as sensitivity analysis to show that the finding was robust?  If so, putting some of that in would be useful.
  %BJC7: make it clear that it is the 280K. Reference all configurations where tilt angles were calculated.

  R-spots originates from the monomer tails.
  %To understand the most likely origin of R-spots, we determined which atoms
  %gave rise to the feature. 
  By removing all non-tail atoms from the trajectory
  and simulating a diffraction pattern with the remaining atoms, we were able to
  isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).

  The tails pack together hexagonally. Since the tails stay nearly flat, we plotted
  their centroids (Figure \ref{fig:centroids}) and measured the angle between
  each centroid and its nearest neighbors with respect to the plane of the
  membrane. We see distinct peaks in the distribution of these angles which are
  consistent with a hexagonally packed configuration
  (Figure~\ref{fig:tail_packing}).

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.32\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.png}
  	\caption{}\label{fig:sandwiched280K}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \includegraphics[width=\textwidth]{tilt_dist.png}
    \caption{}\label{fig:tilt}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
	\centering
	\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
	\caption{}\label{fig:tails_rzplot}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
    \centering
	\includegraphics[width=\textwidth]{centroids_box.png}
  \caption{}\label{fig:centroids}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
        \centering
	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.png}
	        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
        	\centering
	        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
	        \caption{}~\label{fig:layered_integration}
  \end{subfigure}
  \caption{(a) R-spots increases in intensity when the temperature of the system is 
      lowered to 280K. (b) We measured the average angle made between each monomer 
      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
      near -2\degree~which is far from the 37\degree~tilt angle previously used to
      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
      from the trajectory except for carbon atoms that constitute the tails. The
      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
      Since the tails stay relatively flat, we plotted the centroid of each tail 
      and observed that they pack hexagonally (for example, green colored centroids
      in the plot surround the red centroid in hexagonal fashion). (e) We hypothesize
      that R-spots is the result of ordered tail packing. Defining
      the membrane plane to be 0\degree, we measured the angles between each alkane 
      chain tail centroid and its nearest neighbor centroids for the equilibrated 
      sandwiched configuration simulated at 280K. Peaks that appear in each distribution
      are centered near $\pm~33\degree$. (f) We radially integrated the simulated XRD
      patterns of the parallel displaced and sandwiched configuration within the region
      bounding R-alkanes. Peaks appear in the same location as the angle distributions
      which corroborates our hypothesis.}~\label{fig:tail_packing}
  \end{figure}

@@

  The intensity of R-$\pi$ can be calculated from a single trajectory of
  uncorrelated configurations rather than from the average of multiple correlated
  trajectories. Theoretically, in order to mimic the simulated system, we should
  build an initial configuration which has the same amount of quenched disorder
  as our simulations and then create a trajectory to which we add thermal
  disorder to the initial configuration in order to create each frame.
  %BJC9 : The following numbers need to be updated: I want to do 40 trajectories with 1000 frames each for both types of trajectories and compare their mean and uncertainty
  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this
  way was 16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000
  initial configurations, the intensity of R-$\pi$ is 16.42, in close agreement
  with the mean of 40 simulations.  We use the latter method for the remainder of
  this work since we can extract the trends we need using a single trajectory at
  a fraction of the computational cost.

  When we simulated the diffraction pattern of a parallel displaced simple
  system trajectory of 1000 independent configurations, each created using the
  parameters for thermal and quenched disorder in order to place points, the
  $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
  this simple system, and all to follow, 4 times taller in the $z$-direction in
  order to access higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation}
  and~\ref{fig:sf_qz_correlation} shows the $q_y$ and $q_z$ cross-sections of
  R-$\pi$ generated by simulating the structure factor of the trajectory. The
  distance between peaks in the $q_y$ cross-section is equivalent to the distance
  between pores in real space.

@@

%MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
%BJC9: hahaha^
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
  \caption{}\label{fig:sf_qy_nocorrelation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
  \caption{}\label{fig:sf_qy_correlation}
  \end{subfigure} 
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
  \caption{}\label{fig:sf_qz_correlation}
  \end{subfigure}   
  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
  points meant to represent monomer head groups. We added a similar amount of noise to 
  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
  peaks. (b) When we correlate the distance between points within each column, the 
  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
  intensity between the center and outer peaks. (c) Correlation of the distance between
  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
  \end{figure}

  The distances between scatterers within each column are correlated with each
  other. In the simplified system described above, we added Gaussian noise to
  the mean positions of an equally spaced column of points. This ignores any
  interaction head groups might have with each other. To remedy this, we drew
  random samples from a multivariate normal distribution defined by the mean
  positions of an equally spaced column of points. We gave the distribution at
  each point along the column the same standard deviation, $\sigma_z$, shown  in
  by Table~\ref{table:quenched_disorder}. We defined a covariance matrix such
  that the covariance, $v$, of the distance, $d$, between scatterers decays
  exponentially from $v$ according to the equation $ve^{-z/L}$, where $L$ is the
  correlation length. Experimentally, the correlation length can be estimated as
  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$. Accordingly,
  the correlation length of the experimental system is $\geq$ 9 $\AA$. The value
  may be larger since the peak is likely broadened. We simulated the structure
  factor of a simple system built as described above with a correlation length of
  30 $\AA$. We chose 30 $\AA$ in order to exaggerate the effect of correlation
  length for visual purposes. Subsequent structure factor calculations are all
  done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section
  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$
  cross-section (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in
  experiment. Additionally, there is a near 20 \% increase in the maximum
  intensity of R-$\pi$ when the distances between scatterers are correlated.

@@

  Monomers in the ordered basin stack closer together than those in the
  disordered basin (Table~\ref{table:correlation_length}). We calculated the
  equilibrated vertical distance, $\mathit{d}_{equil}$, between monomers using
  Equation~\ref{eqn:decaying_sinusoid}. Monomers in the ordered basin stack ca.
  0.2 and 0.3 \AA~closer than those built in the disordered basin in the
  sandwiched and parallel displaced configurations respectively. The distance
  between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all
  cases, with disordered basins at the high part of that range, 0.2 and 0.3
  \AA~more distant.
  % MRS9: GAFF could OVER predict pi-pi stacking, best to include citations here
  % that it does indeed overpredict.  % BJC9: Turns out the Jankowski group was using oplsaa, not GAFF (they said
  % GAFF to me). Will search for other references.
  This behavior is not surprising since GAFF models atoms as point charges and
  does not appropriately model the aromatic $\pi-\pi$ interactions which would
  make it more energetically favorable for the monomers to stack closer together.
  Additionally, it is possible that the tails prevent close stacking of monomer
  head groups and we do not achieve the timescales necessary for them to
  rearrange into a necessarily more tightly packed configuration. We equilibrated
  the system at 500K in an attempt to coerce the tails into a more tightly packed
  configuration, however we saw no improvement over our 300K models. See section
  S-TBD for details. Overall, head groups in the ordered basin systems pack 
  closest together and are likely the best choice for transport studies.

@@

  The correlation length of the parallel displaced, ordered basin system shows
  the closest agreement with experiment (Table~\ref{table:correlation_length}).
  We calculated the correlation length of each system using
  Equation~\ref{eqn:decaying_exponential}. We could not extract a reliable
  correlation length from the disordered parallel displaced configuration since
  the peaks do not show clear patterns that can easily be fit to an exponential
  decay. The correlation length of both sandwiched systems is relatively low
  because the height of the first peak of $g(z)$ is so high.

% BJC9: omitted because these are not strong points
%  The peak height
%  indicates the degree of local ordering and influences the intensity of R-$\pi$.
%  If vertically adjacent sandwiched head groups were less ordered, which might be
%  achieved with much longer simulations, then the leading peak intensity should
%  decrease and the correlation length would increase. We expect that the leading
%  peak would only get more intense if monomers stacked 3.7 \AA~apart. Conversely,
%  parallel displaced head groups are not as confined by their vertically adjacent
%  neighbors. This z-direction translational freedom may still be feasible if
%  monomers stack 3.7 \AA~apart in a parallel displaced configuration, meaning the
%  system would maintain a correlation length and R-$\pi$ intensity in relative
%  agreement with experiment.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
  thermal noise in the z-direction, however the $q_r$ cross-section profile does
  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
  background intensity, as seen in our simulation (blue) by a factor of 3 when we
  increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$
  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  When we allow monomer columns to move independently in the $z$-direction, the
  intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
  diffraction patterns smooths out. We created simple systems with varying
  amounts of association between columns. In the low limit, the center of mass
  of columns are situated at the same $z$-coordinate. This is how all simple
  systems have been created up to this point. We allow increasing independence of
  columns by randomly shifting each column in the $z$-direction using a uniform
  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges
  between 0 and 1. We limit this discussion to the sandwiched configuration since
  it is not feasible for columns in the parallel displaced configuration, as we
  have set them up, to move past each other. The trends seen above apply to both
  the sandwiched and parallel displaced systems. Allowing columns to move
  independently smooths out the $q_r$ cross-section
  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in
  sharp peaks. The intensity of R-$\pi$ decreases with increasing column
  independence. We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$
  versus when $f=0$. It is likely that the discrepancy between the intensity of 
  R-$\pi$ generated from our simulations versus experiment is due
  to highly correlated columns in our initial configurations.

  \begin{figure}
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr0.png}
  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr75.png}
  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr100.png}
  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
  \end{subfigure}
  \caption{As we increase column independence using the $f$ parameter, the
	  intensity of R-$\pi$ decreases and the $q_r$ cross-section of the simulated
	  diffraction pattern becomes more smooth.  (a) When we place all columns at the
	  same reference $z$ coordinate, $f$ = 0, the intensity of R-$\pi$ is 18.3 and is
	  characterized by sharp Bragg-like peaks. (b) When columns have a moderate
	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
	  still exist. (c) When columns are completely independent, $f$ = 1, the
	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
          relatively smooth.}\label{fig:column_displacement}
  \end{figure}

  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
  cross-section of R-$\pi$ to decrease. Using a system with uncorrelated columns,
  we modified the disorder in both the $r$ and $\theta$ directions by multiplying
  their values by a factor of 0.5 and 2 (Figure~\ref{fig:qy_fwhm}). When we cut
  the noise in half, the FWHM increases by 88 \%. When we double the noise, the
  FWHM decreases by 51 \%.

@@

  We can use what we learned above in order to construct a better model,
  however there will still be shortcomings. We can decrease the intensity of
  R-$\pi$ if we incorporate more $z$-directional noise, which may come from
  increasing the system's temperature. 
  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
  % temperature? Is decreasing the force constant between bonds viable? 
  We can also decrease the intensity of R-$\pi$, in addition to smoothing the
  $q_y$ cross-section by creating initial configurations whose columns are
  displaced randomly in the $z$-direction. We can achieve better averages if we
  create systems with more pores in the unit cell. In order to make head groups
  stack closer together, we can adjust the parameters for aromatic carbons so
  that head groups stack more closely together. Ultimately, we will need
  extremely long simulation times so that monomers within columns can rearrange
  and sample enough independent configurations to generate a robust simulated XRD
  pattern.

  The architecture of each column is likely in between sandwiched and parallel
  displaced. The parallel displaced configuration that we have simulated in this
  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
  stacking mode. The simulated XRD pattern shows faint off-axis features at the
  same $q_r$ value as R-double which is only present in patterns generated from
  parallel displaced configurations. The same feature is present in the
  experimental pattern. The monomers may prefer to be parallel displaced, but
  their displacement is likely only slightly shifted, on the $xy$ plane, from the
  center of mass of their vertically adjacent neighbors. In this way, columns can
  more easily act independently while maintaining a parallel displaced structure.
